Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-01-10 latex/figure3.tex
Set code call parentheses as keyword color

\VariableTok{sim} \OperatorTok{=} \ClassTok{Simulator}\KeywordTok{(\ClassTok{Oscillator})}
\VariableTok{df} \OperatorTok{=} \VariableTok{sim}.\FunctionTok{solve}\KeywordTok{(}\VariableTok{save\_at}\OperatorTok{=}\ClassTok{np}.\FunctionTok{linspace}(\ValueTok{0}, \ValueTok{5}, \ValueTok{101})\KeywordTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

\VariableTok{sim} \OperatorTok{=} \ClassTok{Simulator}\KeywordTok{(\ClassTok{Oscillator})}
\VariableTok{df} \OperatorTok{=} \VariableTok{sim}.\FunctionTok{solve}\KeywordTok{(}\VariableTok{save\_at}\OperatorTok{=}\ClassTok{np}.\FunctionTok{linspace}\KeywordTok{(}\ValueTok{0}, \ValueTok{5}, \ValueTok{101}\KeywordTok{))}
\end{Highlighting}
\end{Shaded}
